White Wine Quality Exploratory Data Analysis by Zongran Luo
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(GGally)
library(gridExtra)
library(psych)
library(reshape2)
library(dplyr)
library(memisc)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
df <- read.csv("https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityWhites.csv")


```

The data set we are going to dig is publicly available for research. The details 
are described in the following:

P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. 
Modeling wine preferences by data mining from physicochemical properties.
In Decision Support Systems, Elsevier, 47(4):547-553. ISSN: 0167-9236.

This data set has 13 variables with 4898 observatons. This data set mainly covered 
properties of white wines, including index variables, qualities, density and
10 other properties.

The goal of this project is to understand and analyze this data set. In particular, 
I will try to find answers of the following three questions:

* Find the typical range and distributino of properties and qualities of wines.
* Find the properties that most influence qualities of wines.
* Find relationships between properties and find out if any correlations exist 
between qualities and properties.


# Univariate Plots Section


I will first take a look at the dimensions, field names and the whole stucture of
the data set.

```{r echo=FALSE, Univariate_Plots}
str(df)
```

Our data set consists of 13 variables, with 4898 observations.

From the statement of the data set, each description of variable could be found 
and I will go through the ditribution of each variable, and this will help us 
understand the data set better.

##### Quality Distribution

The quality is from a median of at least 3 evaluations made by wine experts.

**Summary**
```{r}
summary(df$quality)
```


```{r}
ggplot(df,aes(x = quality))+
  geom_histogram(binwidth = 0.1)+
  scale_x_continuous(breaks = seq(1,10,1))
```
I set the binwidth to be 0.1 and the range of quality could be between 0 and 10, 
0 the worst and 10 the best. We can find there are no wines graded 0, 1, 2 or 10.
And we can make a table to see if we have any decimals in this varaible.
```{r}
table(df$quality)
```
This variable could be transfered to factor with sequence, so I add quality.discrete
to keep quality in the format of factor.
```{r}
df$quality.discrete <- factor(df$quality,ordered = T)
```



##### Fixed Acidity (gram/liter)

Fixed acidity is most acids involved with wine or fixed or nonvolatile. Its mean
and median are very close and the distribution is very normally distributed.

**Summary**
```{r}
summary(df$fixed.acidity)

```


```{r}
summary(df$fixed.acidity)
ggplot(aes(x= fixed.acidity), data = df)+
  geom_histogram(binwidth = 0.1)
```

We can see the range is between 3.8 and 14.2, but there are 50% of the data between
6.3 and 7.3. We can see the graph is rather symmetric and normally distributed.


##### Volatile Acidity(gram/liter)

From the statment of data set, I found volatile acidity is the amount of acetic 
acid in wine, which at too high of levels can lead to an unpleasant, vinegar taste. 

**Summary**
```{r}
summary(df$volatile.acidity)
```
We can see volatile acidity has small range and so I will set the binwidth to 0.01.

```{r}
# ggplot(aes(x = volatile.acidity, fill = quality), data = df)+
#   geom_histogram(binwidth = 0.01)+
#   facet_wrap(~quality,scales = "free_y")
ggplot(aes(x = volatile.acidity), data = df)+
  geom_histogram(binwidth = 0.01)
```

Though we can recognize it is normally distributed, but the graph is positively 
skewed and I will plot log scale on x axis.

```{r}
ggplot(aes(x= volatile.acidity), data = df)+
  geom_histogram(binwidth = 0.01)+
  scale_x_log10(breaks = seq(0,1,0.1))

```
We can see it is more normallized distributed. due to its less density in the lower
part, we can see some in the graph with lower acidity are very low or even 0, but
it does not affect the distribution.

```{r}
# ggplot(aes(x= quality, y = volatile.acidity), data = df)+
#   geom_point(stat = "summary", fun.y = median)
#   geom_line(stat='summary', fun.y = mean)

```


##### Citric Acid(gram/liter)
From the statment of data set, I found citric acid has small quantities and can add 
'freshness' and flavor to wines.

**Summary**

```{r}
summary(df$citric.acid)
```

Found the variable has small range, and so I set the bin widith to 0.01. Since it 
is positively skewed, I will put square on the x scale.

```{r}
ggplot (aes(x = citric.acid), data =df)+
  geom_histogram(binwidth =  0.01)+
  scale_x_sqrt(breaks = seq(0,1.6,.1))
```

Though we can see to normalization, the wines with citric acid of 0.5 has a much larger 
amount than others around it.

##### Residual Sugar(gram/liter)
From the statment of data set, residual sugar is the amount of sugar remaining after 
fermentation stops. Wines with less than 1 gram/litter are rare but with more than 
45 grams/litter are considered sweet.

**Summary**

```{r}
summary(df$residual.sugar)
```

The histogram is positively skewed and so I log the scale of x axis.

```{r}
ggplot(aes(x = residual.sugar), data =df )+
  geom_histogram(binwidth = 0.1)+
  scale_x_log10(breaks = c(seq(1,10,1),seq(20,60,10)))

```
We can see there are two peak for residual sugar, one is between 1 and 2 and the 
other is between 7 and 15.

Since wines with sugar more than 45 grams/liter are considered sweet, I would create a another categorical variable, "Sweet", to identify if the wine is sweet or not.

```{r}
df$Sweet <- df$residual.sugar > 40
```


##### Free Sulfur Dioxide and Total Sulfur Dioxide (milligram/liter)

In the statement of the data set, free sulfur dioxide is the free form of SO2 exists 
in equilibrium between molecular SO2 (as a dissolved gas) and bisulfite; it prevents 
microbial growth and the oxidation of wine.

Total sulfur dioxide is the amount of free and bound forms of S02; in low concentrations, 
SO2 is mostly undetectable in wine, but at free SO2 concentrations over 50 mg/L, SO2 
becomes evident in the nose and taste of wine.

**Summary**

Free sulfur dioxide

```{r}
summary(df$free.sulfur.dioxide)
```

Total sulfur dioxide
```{r}
summary(df$total.sulfur.dioxide)
```


```{r}
pfree <- ggplot(aes(x = free.sulfur.dioxide), data =df)+
  geom_histogram(binwidth = 1)
ptotal <- ggplot(aes(x = total.sulfur.dioxide), data = df)+
  geom_histogram(binwidth = 1)

grid.arrange(pfree, ptotal)

```

We can see though these two variables are related and both are normally distributed,
they seem to not have the same distribution. I will discuss more in the next session.

Since free SO2 will affect nose and taste of wine.I will create a new categorical variable to separate wines which can affect taste with SO2 and the other do not.

```{r}
df$SO2.effect <- df$free.sulfur.dioxide > 50
```


##### Sulphates (potassium sulphate - gram / liter)
Sulphates is a wine additive which can contribute to sulfur dioxide gas (S02) levels, 
which acts as an antimicrobial and antioxidant

**Summary**
```{r}
summary(df$sulphates)
```
```{r}
ggplot(df, aes(x = sulphates))+
  geom_histogram(binwidth = 0.01)
```

We can see sulphate is normally distributed here.

##### pH
In this data set, pH value describes how acidic or basic a wine is on a scale from 
0 (very acidic) to 14 (very basic); most wines are between 3-4 on the pH scale.

**Summary**

```{r}
summary(df$pH)
```
We can see we have some wines with ph under 3 but no one exceeds 4.

```{r}
ggplot(df,aes(x = pH))+
  geom_histogram(binwidth = .01)
```
This variable is normally distributed.




##### Density (gram/centimeter^3)
The density of water is close to that of water depending on the percent alcohol 
and sugar content.
**Summary**
```{r}
summary(df$density)
```
It is not supprise that the density has a very small range between .9871 and 1.0390.
As described in the definition above of density in this data set, it is very close
to water depending on its components, alcohol and sugar.
```{r}
ggplot(df, aes(x = density))+
  geom_histogram(binwidth = 0.0001)
```
We can see except for some with relatively high density,all of the rest concentrating 
on the range between .99 to 1.00.


######Alcohol

In this data set, alcohol is the percent alcohol content of the wine.

**Summary**
```{r}
summary(df$alcohol)
```

The alcohol has a distribution between 8% and 14%.

```{r}
ggplot(df, aes(x = alcohol))+
  geom_histogram(binwidth = .1)+
  scale_x_continuous(breaks = seq(0,15,0.5))
```
Most wines have the alcohol between 9% and 9.5%, with gradually fewer wines of higher 
alcohol. 

##### Chlorides (gram/liter)
Chlorides are the amount of salt in the wine.

```{r}
summary(df$chlorides)
```

```{r}
ggplot(df, aes(x = chlorides))+
  geom_histogram(binwidth = 0.01)+
  scale_x_log10(breaks= seq(0,.4,0.05))
```

I have made the logarithmic scale for the x axis and we can see that wines generally 
have chlorides under 0.1g/L. 


# Univariate Analysis


### What is the structure of your data set?

This data set has 4898 white wine observations with 13 variables in total, including
index variable x, "quality" variable and 11 properties of white wines(fixed acidity, volatile acidity, citric acid, residual sugar, chlorides, free sulfur dioxide, total sulfur dioxide, density, pH, sulphates and alcohol). 

The quality is transfered to ordered factor variables with the following levels:

worst ----->  best
quality: 0,1,2,3,4,5,6,7,8,9,10

Other observations:

* Most features of wines are normally distributed.
* All wines are graded from 3 to 9
* Over 3600 wines were graded with 5 or 6 points.


### What is/are the main feature(s) of interest in your data set?

The main feature of this data set is the quality. 11 properties of wines could all 
affect the final grade. It looks like the quality could be predictable from these
11 properties.Though a regression model could be created for prediction, we still
need to consider correlations between properties.


### What other features in the data set do you think will help support your \
investigation into your feature(s) of interest?

All other features can support me on the investigation, but we still need to consider
correlations and see if we need to eliminate any variables.

### Did you create any new variables from existing variables in the data set?

I created two new categorical variable, SO2.effect and Sweet. SO2.effect is to record
wines which have free SO2 concentratoions over 50 ppm and Sweet is to record wines 
which have sugar over 45 g/L. These wines are considered sweet.

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?
The original format of the variable of quality is integer, but the quality is a 
ordered level from 0 to 10, so I transgered it from integers to factors with ordered
leveland named it quality.discrete. Therefore, the quality.discrete variabel in 
the data set is factors with 7 levels from 3 to 9, due to lack of data with quality
of 0, 1, 2 and 10.


# Bivariate Plots Section

In this part, I will first make a matrix of plots with the data set of white wine.
In this matrix plot, we can find point plots of any two properties and boxplots and 
bar charts of qualities. 


```{r}
pairs.panels(df[2:13])
res <- cor(df[2:13])
```



```{r}
correlations <- melt(res,varnames = c('property1','property2'),value.name = 'correlation')
correlations <- correlations[!duplicated(correlations$correlation),]
correlations <- arrange(correlations,desc(abs(correlation)))
correlations[abs(correlations$correlation)>0.4 & correlations$correlation!=1, ]
```


I pick the pairs with correlations more than 0.4 and I found some properties are 
correlated. Density and residual sugar has the correlations of 0.839, while density 
and alcohol has the correlations of-o.78. Total sulfur dioxide and free sulfur 
dioxide  have the correlations of 0.616.

The higher the residual sugar is, the higher the density will be. On the other hand,
the higher the alcohol is, the lower the density will be. That makes sense since
alcohol has a lower density while sugar has a higher density. We can also see that 
total sulful dioxide is positively related to free sulfur dioxide. The wine with more 
sulful dioxide in total generally wil have more free sulful dioxide. 

I want to see how the properties are related to the quality. I will make boxplots 
for all the properties v.s. quality.

```{r}
df_melt <- melt(df,"quality.discrete")
ggplot(subset(df_melt,variable != 'X'),aes(quality.discrete,value)) +
  geom_boxplot() +
  facet_wrap(~variable, scales = "free_y")
```

From the boxplot matrix, we can find some trends of qualities.Volatile acidity, free 
and total sulfur dioxide,
##### pH v.s. Quality
The high quality generally has relatively high pH value. With the quality increasing, 
we can see the pH value is increasing as well.
```{r}

ggplot(df,aes(x = quality.discrete, y =pH))+
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)
```



##### Density, Alcohol, Residual Sugar v.s Quality

It looks high quality has a lower density from the graph above, but I will get rid
of some outlier to see it more clearly.
```{r}

ggplot(df,aes(x = quality.discrete, y =density))+
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  scale_y_continuous(limits = c(0.985,1.005))+
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)
```
We can see high quality comes with lower density. Since we found density is very 
related to alcohol and residual sugar, I will see what it looks like if I have alcohol
 and residual v.s. quality separately.
 
 
```{r}

alcohol <- ggplot(df,aes(x = quality.discrete, y =alcohol))+
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)

sugar <- ggplot(df,aes(x = quality.discrete, y =residual.sugar))+
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  ylim(0,20)
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)

grid.arrange(alcohol, sugar)
```
The trend is clear and reflect the correlation of density to alcohol and residual
sugar. A wine with high quality generally has higher alcohol and lower residual 
sugar.


##### Volatile Acidity v.s. Quality

I will create boxplots for each quality to demonstrate volatile acidity of each wine.
Red points are outliers and their alpha value is 0.2, and so the darker the part 
is, the more points there. The green cross is the mean of that category.

```{r echo=FALSE, Bivariate_Plots}

ggplot(df,aes(x = quality.discrete, y = volatile.acidity))+
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)

```
In the boxplots, we can see the medians are around 0.3. But if we see the outliers,
we can find the value of outliers, except for the quality of 3, are decreasing while 
the quality is getting higher.
```{r}
table(df$quality)
```

Though the quality of 3 has no outliers, it does not mean quality of 3 does not have 
high volatile acidity. Quality is affected by other properties and in quality of 3,
the data set does not have enough size of sample.


##### Free and Total Sulfur Dioxide v.s. Quality


```{r}

ggplot(subset(df_melt,variable == 'free.sulfur.dioxide' | variable == 'total.sulfur.dioxide'),aes(quality.discrete,value)) +
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)+
  facet_wrap(~variable, scales = "free_y")

```


##### Free sulfur dioxide summary
```{r}
by(df$free.sulfur.dioxide,df$quality.discrete,summary)
```

##### Total sulfur dioxide summary

```{r}
by(df$total.sulfur.dioxide,df$quality.discrete,summary,)
by(df$total.sulfur.dioxide,df$quality.discrete,IQR)
```


The trend between sulfur dioxide and quality is clear. Wines with high quality are 
less various in sulfur dioxide. We can see with the quality increasing, the range 
of sulfur dioxide is decreasing, also its median and mean are both decreasing as 
well.

```{r}
test <-  lm(formula = density ~　alcohol+residual.sugar,data = subset( df, density <= quantile (df$density,0.999)))
summary(test)
```


# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the data set?

From the data set, we can find wines with high quality generally have lower density,
residual sugar, sulfur dioxide and higher pH value and and alcohol. 

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

Density is very related to residual sugar and alcohol. Density has the correlation
of 0.84 with sugar and -0.78 with alcohol. More sugar will bring the density up and 
more alcohol will lower the density.
I will discuss it later in multivariate analysis.

### What was the strongest relationship you found?

Among all the correlations, the strongest relationship is density and sugar.That 
makes sense and more sugar will increase density.

# Multivariate Plots Section

I split the data into 7 plots, which represents 7 different qualities, 3 to 9, in the data
set.

```{r}
ggplot(df,aes(x = total.sulfur.dioxide, y = free.sulfur.dioxide))+
  xlim(quantile(df$total.sulfur.dioxide,0.01),quantile(df$total.sulfur.dioxide,0.99))+
  ylim(quantile(df$free.sulfur.dioxide,0.01),quantile(df$free.sulfur.dioxide,0.99))+
  scale_x_sqrt()+
  scale_y_log10()+
  geom_point(alpha = 0.2)+
  facet_wrap(~quality.discrete)
```

```{r}
ggplot(df,aes(x = alcohol, y = density, color = quality.discrete))+
  scale_x_sqrt()+
  scale_y_log10()+
  geom_point(alpha = 0.2)+
  facet_wrap(~quality.discrete)
```

From the graph above, we can see with the quality increasing, the quality is more 
likely to increase with the quality decreasing. Also, the quality will increase with
alcohol increasing as well. 

SO2 will influence the taste and smell if free SO2 concerntration is over 50 pps.

```{r}
so2effect <- data.frame(table(df$quality,df$SO2.effect))
so2effect <- dcast(so2effect,Var1~Var2)
names(so2effect) <- c('Quality','No_SO2effect','SO2effect')
so2effect$so2effectratio <- round(so2effect$No_SO2effect/(so2effect$No_SO2effect+so2effect$SO2effect),2)

so2effect
```
For each quality, the ratio of SO2 effect is between 75% and 91%, and they are 
hard to have a trend.

```{r}
ggplot(df,aes(x = density, y = total.sulfur.dioxide, color = SO2.effect))+
  scale_x_continuous(limits = c(.985,1.01))+#quantile(df$density,0.01),quantile(df$density,0.99))+
  # ylim(quantile(df$density,0.01),quantile(df$density,0.99))+
  geom_point()+
  facet_wrap(~quality.discrete)
```


```{r}
m1 <-  lm(formula = quality~ fixed.acidity,data = subset( df, density <= quantile (df$density,0.999)))
m2 <- update(m1, ~. +volatile.acidity)
m3 <- update(m2, ~. +citric.acid)
m4 <- update(m3, ~. +residual.sugar)
m5 <- update(m4, ~. +chlorides)
m6 <- update(m5, ~. +free.sulfur.dioxide)
m7 <- update(m6, ~. +total.sulfur.dioxide)
m8 <- update(m7, ~. +density)
m9 <- update(m8, ~. +pH)
m10<- update(m9, ~. +sulphates)
m11<- update(m10, ~. +alcohol)
mtable(m6,m7,m8,m9,m10,m11)
```

None of These models seem to be a good fit. Though the model with all variables has
a low p value, which means this model works but it can only explain about 30% of 
the data, which is still very low. That makes no sense to furthur remove varaibles 
to get a more precise model. The table is showing models with 6 to 11 variables. 
None of these models have a good enough adj. R-squared value. Though these models 
have low p value and variables have some effect but the variability cannot be explained
very well due to low R squares. 


I found density has high correlations with residual sugar and alcohol. I will try to
see if they have any visiable relationships and then create a model.
```{r}
ggplot(df[df$density < quantile(df$density,0.99) ,],aes(x = alcohol, y = residual.sugar, color = density))+
  # ylim(quantile(df$density,0.01),quantile(df$density,0.99))
  geom_point()+
  facet_wrap(~quality.discrete)+ scale_colour_gradient(low = "green", high = "red")
```


I will first take a look at density to see its relationships with sugar and alcohol.
Wines with more residual sugars have lighter color, and so they are denser than the 
ones with lower sugar. Also, wines with more alcohol are darker, or less dense, than
wines with less alcohol.

```{r echo=FALSE, Multivariate_Plots}

test <-  lm(formula = density~ alcohol+ residual.sugar,data = subset( df, density <= quantile (df$density,0.999)))
summary(test)

```

Based on the r-squared, alcohol and residual.sugar can explain 91.8 percent of the
variance in density.


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

I found quality would increase with density going down.I found a high SO2 may affect
the tatse and smell of wines and so I assumed it might affect the quality. I created 
a variable, SO2effect, which recorded if wines have free SO2 over 50 ppm which might
affect the taste of wines. However, from the table of SO2 and quality. A trend cannot
be seen by looking the no_so2effect in the table. I assumed that it should be getting
higher with higher qualities, but the fact is that is not the trend. It looks like 
smell and taste from SO2 do not influence the quality alone.

### Were there any interesting or surprising interactions between features?
For other features, I try to test alcohol with density and alcohol. As I expected 
earlier, alcohol is very realted to density and alcohol and the model can 
help the model of density to explain 91 percent of the data.

### OPTIONAL: Did you create any models with your data set? Discuss the \
strengths and limitations of your model.

I created two models of regression, one for the quality and the other for density.
The model of quality cannot explain the variability effectively due to a low R square.
However, the model of density can explain 91 percent of the variability and this 
is a good model.


------

# Final Plots and Summary


### Plot One
```{r echo=FALSE, Plot_One}
ggplot(df,aes(x = quality))+
  geom_histogram(binwidth = 0.1)+
  scale_x_continuous(breaks = seq(1,10,1))

```

### Description One
In this histogram, we can find the quality is normally distributed and I set the 
bin width to 0.1 and it looks like it only has itegers and we can find that is true
after look back into the data. Data in quality 3 and 9 need our attention since these
samples do not have big size and they may not be representative.

### Plot Two
```{r echo=FALSE, Plot_Two}
alcohol <- ggplot(df,aes(x = quality.discrete, y =alcohol))+
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)

sugar <- ggplot(df,aes(x = quality.discrete, y =residual.sugar))+
  geom_boxplot( outlier.colour = 'red', outlier.alpha = 0.2)+
  ylim(0,20)
  geom_point( stat = 'summary' , fun.y = mean, color = 'green', shape = 4, show.legend = T)

grid.arrange(alcohol, sugar)
```

### Description Two
We can see that generally quality of wines increase when alcohol increases. And 
wines with more sugar will have lower quality as well. However, these trends are 
not very clear since we still have exceptions in the sample of wines with quality 
4 and 3.


### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(df[df$density < quantile(df$density,0.99) ,],aes(x = alcohol, y = residual.sugar, color = density))+
  # ylim(quantile(df$density,0.01),quantile(df$density,0.99))
  geom_point()+
  facet_wrap(~quality.discrete)+
  scale_colour_gradient(low = "green", high = "red")
```

### Description Three
The plots are splitted in qualities. We can find wines with high quality have more 
alcohol comparing to residual sugar, and wines with lower quality have more sugar
instead.


# Reflection


The data set contains information on 4898 lines across 13 variables. I started by 
understanding the individual variables in the data set and then I explored bivariated
plots and find correlations between variabales. Eventually, I explored the quality 
across multiple variables and created a linear model to predict winte qualities.

This data set has 1 index, 1 quality and 11 properties. I was supprised 10 out of 
11 properties were normally distributed. Every property has some relationship with 
quality, but the linearity is not clear. The most clear trend with quality I can 
find is alcohol. Quality has the positive linearity with alcohol, but the trend does 
not work for wines with low quality. Also It was not supprised to see that density 
has high correlations with residual sugar and alcohol. Generally, the linear model
for quality does not have clear trend and cannot explain the variability of the 
properties.

Limitations of this model include the source of data. We find the distribution of
quality is normally distributed. It means the data set does not have enough sample 
in of wines with lowest quality and highest quality. Also methodology is another 
limit since from what I observe, quality might not be linearly related to current
variables. We can have some discriptive summary here, but if we want to go for 
predictions, we might need to use machine learning which might be more helpful in 
predictions. 
